quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-08-18 paper-quollr.Rmd
Updated the annotations

scurve_umap_plt_select1 <- ggplot(
  scurve_umap_scaled_select1_deselected, 
  aes(x = emb1, y = emb2)) +
  geom_point(alpha = 0.5, color = clr_choice, size = 0.5) +
  geom_point(data = scurve_umap_scaled_select1_selected, aes(x = emb1, y = emb2), alpha = 0.5, color = "#756bb1", size = 0.5) +
  interior_annotation("a1") +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

scurve_umap_plt_select2 <- ggplot(
  scurve_umap_scaled_select2_deselected, 
  aes(x = emb1, y = emb2)) +
  geom_point(alpha = 0.5, color = clr_choice, size = 0.5) +
  geom_point(data = scurve_umap_scaled_select2_selected, aes(x = emb1, y = emb2), alpha = 0.5, color = "#756bb1", size = 0.5) +
  interior_annotation("b1") +
  xlim(sc_xlims) +
  ylim(sc_ylims)
```

```{r, eval=knitr::is_latex_output(), fig.pos='H'}
scurve_umap_plt_select1 + scurve_umap_plt_select1 +
  scurve_umap_plt_select2 + scurve_umap_plt_select1 +
  plot_layout(ncol = 2)
```

@@

```{r, eval=knitr::is_latex_output()}
error_plot_scurve_hist1 + scurve_umap_plt_select1 + scurve_umap_plt_select1 +
  error_plot_scurve_hist2 + scurve_umap_plt_select2 + scurve_umap_plt_select1 +
  plot_layout(ncol = 3)
```

>>>>

scurve_umap_plt_select1 <- ggplot(
  scurve_umap_scaled_select1_deselected, 
  aes(x = emb1, y = emb2)) +
  geom_point(alpha = 0.5, color = clr_choice, size = 0.5) +
  geom_point(data = scurve_umap_scaled_select1_selected, aes(x = emb1, y = emb2), alpha = 0.5, color = "#756bb1", size = 0.5) +
  xlim(sc_xlims) +
  ylim(sc_ylims)

scurve_umap_plt_select1_lk <- scurve_umap_plt_select1 +
  interior_annotation("a1")

scurve_umap_plt_select1_lk2 <- scurve_umap_plt_select1 +
  interior_annotation("a2")

@@

scurve_umap_plt_select2 <- ggplot(
  scurve_umap_scaled_select2_deselected, 
  aes(x = emb1, y = emb2)) +
  geom_point(alpha = 0.5, color = clr_choice, size = 0.5) +
  geom_point(data = scurve_umap_scaled_select2_selected, aes(x = emb1, y = emb2), alpha = 0.5, color = "#756bb1", size = 0.5) +
  xlim(sc_xlims) +
  ylim(sc_ylims)

scurve_umap_plt_select2_lk <- scurve_umap_plt_select2 +
    interior_annotation("b1")

scurve_umap_plt_select2_lk2 <- scurve_umap_plt_select2 +
    interior_annotation("b2") 
```

```{r, eval=knitr::is_latex_output(), fig.pos='H'}
scurve_umap_plt_select1_lk + scurve_umap_plt_select1 +
  scurve_umap_plt_select2_lk + scurve_umap_plt_select1 +
  plot_layout(ncol = 2)
```

@@

```{r, eval=knitr::is_latex_output()}
error_plot_scurve_hist1 + scurve_umap_plt_select1_lk2 + scurve_umap_plt_select1 +
  error_plot_scurve_hist2 + scurve_umap_plt_select2_lk2 + scurve_umap_plt_select1 +
  plot_layout(ncol = 3)
```
